\documentclass[10pt]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{mathptmx}

\begin{document}

\setlength{\parskip}{1mm}
\pagenumbering{gobble}

\newcommand{\name}[1]{
  \begin{center} \LARGE \textbf{#1} \end{center}
}

\newcommand{\contact}[1]{
  \begin{center} \large #1 \end{center}
}

\newcommand{\sectiontitle}[1]{
  \rule{\columnwidth}{1pt}
  \par\nointerlineskip
  { \large \textbf{#1} }
  \par\nointerlineskip
  \rule{\columnwidth}{3pt}\par
}

\newcommand{\employer}[2]{
  \noindent \textbf{#1} \hfill \textbf{#2} \par
}

\newcommand{\job}[2]{
  \noindent \textit{#1} \hfill #2 \par
}

\newcommand{\bullettitle}[1]{
  \textit{#1}:
}

\newenvironment{bullets}{
  \begin{itemize}
}{
  \end{itemize}
  \vspace{0.05in}
}

\name{CHRISTIAN SMITH}
\contact{cesm@umich.edu \textbar \hspace{0.1mm} Allen Park, MI 48101 \textbar \hspace{0.1mm} 734-308-5175}

\sectiontitle{EDUCATION}

\employer{University of Michigan}{Ann Arbor, MI}
\job{M.S.E. in Computer Science}{December 2018}
\job{B.S.E. in Computer Science, Minor in Mathematics}{December 2017}
\begin{bullets}
  \item \bullettitle{GPA} 4.00/4.00
  \item \bullettitle{Coursework} Object-Oriented and Advanced Programming, Introduction to Operating Systems,
        Web Databases and Information Systems, Introduction to Computer Security, Database Management Systems,
        Data Structures and Algorithms
  \item \bullettitle{Awards} Eta Kappa Nu EECS Honor Society, EECS Scholar Award, College of Engineering
      Dean's List
\end{bullets}

\sectiontitle{WORK EXPERIENCE}

\employer{Allston Trading}{Chicago, IL}
\job{Software Developer Intern}{May 2017 -- Jul. 2017}
\begin{bullets}
  \item Developed a high performance, real time, tick level charting library using OpenGL bindings for Java.
        The library is used daily by traders to view market data and is capable of rendering millions of points
        at framerates several times higher than the charting library it replaced.
  \item Wrote a limit order book server in C++ for testing internal trading applications. The server communicates
        with trading clients via the FIX protocol, and with a web client that can be used to manually accept, fill,
        etc. orders using WebSockets.
  \item Created a C++ server that exposes the functions and callbacks of an internal trading framework to clients
        via WebSockets.
  \item Built a web client using React and Redux to provide a GUI for the two C++ servers mentioned above. The client
        can display market data in real time and allows developers to test an internal trading framework using a GUI
        in a web browser.
\end{bullets}

\employer{University of Michigan -- EECS Department}{Ann Arbor, MI}
\job{Instructional Aide for EECS 482 (Introduction to Operating Systems)}{Jan. 2017 -- Present}
\begin{bullets}
  \item Lead weekly discussion sessions of approximately 30 students intended to review and clarify material
        from lectures.
  \item Hold regular office hours to assist students in exam preparation and completion of programming projects.
  \item Answer questions on an online course discussion board, where over 50 questions are posted per day
        new project deadlines.
\end{bullets}

\employer{University of Michigan -- Climate and Space Sciences and Engineering Department}{Ann Arbor, MI}
\job{Web Development Intern}{Apr. 2016 -- Dec. 2016}
\begin{bullets}
  \item Created a prototype for an educational browser game in which users attempt to reproduce a given wind
        pattern by repositioning air pressure points on a map.
  \item Designed and implemented the front-end of the game using web technologies such as React, Redux, and
        HTML5 canvas.
  \item Wrote and deployed a Node.js and MySQL back-end for the game which manages user accounts, scenarios
        for players to attempt to recreate, and high scores or each scenarios.
\end{bullets}

\employer{University of Michigan -- Computer Aided Engineering Network}{Ann Arbor, MI}
\job{Hotline Consultant}{Feb. 2016 -- Dec. 2016}
\begin{bullets}
  \item Created a web-based digital signage display to show upcoming hours of operation and service status using
        HTML, CSS, and JavaScript, and configured a Raspberry Pi to run the display in a web browser.
  \item Wrote a Chrome extension to automatically refresh the helpdesk's internal ticketing website, search the
        HTML document for new tickets, and push desktop notifications when new tickets are present.
  \item Assisted student and faculty users with computer labs, software, and user accounts by phone, email, live
        chat, and in person.
\end{bullets}

\sectiontitle{SKILLS}
\begin{bullets}
  \item \bullettitle{Languages} C++, Python, Java, JavaScript, HTML, CSS, SQL
  \item \bullettitle{Technologies} Git, Node.js, Express, React, Redux, ES6, JOGL, WebSockets
  \item \bullettitle{Operating Systems} Windows, Linux
\end{bullets}

\end{document}
